### 2024-07-11 README.Rmd
Pour André

ggplot() +
  # plot the spatraster first
  geom_spatraster(
    data = travel_time_sin
  ) +
  theme_minimal() +
  scale_fill_whitebox_c(palette = "deep") +
  # overlay the vector outline
  geom_spatvector(
    data = sin,
    colour = "khaki3",
    linewidth = 1,
    fill = NA
  ) +
  # add the points from tibble
   geom_point(
     data = changi_airport,
     aes(x = x, y = y)
   ) +
  labs(x = NULL, y = NULL, fill = "Travel time\n(minutes)")

>>>>

ggplot() +
  # plot the spatraster first
  geom_spatraster(
    data = travel_time_sin
  ) +
  theme_minimal() +
  scale_fill_whitebox_c(palette = "deep") +
  # overlay the vector outline
  geom_spatvector(
    data = sin,
    colour = "grey70",
    linewidth = 1,
    fill = NA
  ) +
  # add the points from tibble
   geom_point(
     data = changi_airport,
     aes(x = x, y = y),
     colour = "hotpink"
   ) +
  labs(x = NULL, y = NULL, fill = "Travel time\n(minutes)")
